Covariate Analysis of MAYO Reprocessed counts Regressing out Diagnosis as well for TWAS

### 2020-05-23 code/prepscripts/MSBB_TranscriptNorm.Rmd
File Paths Fix

Distribution of samples are: `r kable(tmp)`

@@

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp  <- synapseclient$Synapse()
syn_temp$login()
setwd("~/AD_TargetRank/code/")
source("~/AD_TargetRank/utilityFunctions/knitfile2synapseClient.R")
source("~/AD_TargetRank/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "MSBB_TranscriptNorm.Rmd",
                                          parentId ="syn22092490",
                                          folderName = 'MSBB')
```

>>>>

@@

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp  <- synapseclient$Synapse()
syn_temp$login()
setwd("~/AD_TargetRank/code/")
source("~/AD_TargetRank/utilityFunctions/knitfile2synapseClient.R")
source("~/AD_TargetRank/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "~/AD_TargetRank/code/prepscripts/MSBB_TranscriptNorm.Rmd",
                                          parentId ="syn22092490",
                                          folderName = 'MSBB')
```

### 2020-05-23 code/prepscripts/Mayo_TranscriptNorm.Rmd
File Paths Fix

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp  <- synapseclient$Synapse()
syn_temp$login()
setwd("~/AD_TargetRank/code/")
source("~/AD_TargetRank/utilityFunctions/knitfile2synapseClient.R")
source("~/AD_TargetRank/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "Mayo_TranscriptNorm.Rmd",
                                          parentId ="syn22092490",
                                          folderName = 'Mayo')
```

>>>>

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp  <- synapseclient$Synapse()
syn_temp$login()
setwd("~/AD_TargetRank/code/")
source("~/AD_TargetRank/utilityFunctions/knitfile2synapseClient.R")
source("~/AD_TargetRank/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "~/AD_TargetRank/code/prepscripts/Mayo_TranscriptNorm.Rmd",
                                          parentId ="syn22092490",
                                          folderName = 'Mayo')
```
